parameters

### 2020-02-07 manuscript/drafts/manuscript.Rmd
performed first simulation study

Hyperparameters
  * alpha - accounts for features not present in learning samples and prevents zero probabilities in further computations. ?

@@

>>>>

Hyperparameters

  * alpha - accounts for features not present in learning samples and prevents zero probabilities in further computations.

@@

## amount of training data
n_instances = number of papers queried each query
n_queries = number of queries
n_prior_included: 5
n_prior_excluded:
